The Globular Cluster System of the Auriga Simulations

### 2019-05-09 AurigaGCS.tex
Updates for 4.1

\subsection{Metallicity distribution}
\label{sec:results_FeH}
We investigate whether the star formation model implemented in Auriga produces 
metallicity distributions consistent with the MW (M31) GC system, and whether 
the subgrid generates sufficient total mass to account for the bound cluster 
formation efficiency and evolutionary mass loss.

\begin{figure}
    \includegraphics[width=\columnwidth]{{FeH_mu_sigma}.png}
    \caption{
        First vs second central moment of the Auriga L4 metallicity distributions.
        Each dot represents one simulation for a given colour. The orange (blue) 
        [red] dots shows the values calculated using the old (old insitu) 
        [old accreted] star particles. Orange triangles indicate that all stars 
        were used. The purple (magenta) cross denotes our calculation using all 
        MW (M31) observations (i.e. asuming a unimodal distribution). The black 
        solid (open) dots indicate the literature values of a bimodal Gaussian 
        fit to the data \citep[values from][p. 38]{1998gcs..book.....A},
        showing the the metal-rich (metal-poor) component of the MW.
        \label{fig:FeH_mu_sigma}
    }
\end{figure}
Figure~\ref{fig:FeH_mu_sigma} shows the mean and standard deviation of the
[Fe/H] distribution of star particles in the Auriga L4 simulations. One dot 
of a given colour shows one particular simulation (thirty in total). The 
orange (blue) [red] dots represent the distributions of old (old insitu) 
[old accreted] star particles, and orange triangles indicate that all stars
were used. The mean metallicities of all GC candidates (orange dots) lie in the 
range $-0.95$ to $-0.4$, which is lower than when we include all star particles 
(orange triangles, centred around $\mu \sim 0$). Furthermore we find that the 
distributions of the accreted (insitu) GC candidates shift to slightly lower 
(higher) values and seem to be roughly centred around $\mu \sim -0.5$ ($-0.8$)
We find this trent that the distribution is more metal-poor (metal-rich)
when splitting the GC candidates into accreted (insitu) populations for the
majority of the Auriga simulations. The only exceptions are Au4-1 where this 
trent is reversed, and Au4-7 where all three (sub)populations have $\mu \sim -0.82$

The purple (magenta) cross shows the values calculated using all MW (M31) GC
observations (i.e. assuming a unimodal distribution). The black solid (open) dots
mark the literature values of a bimodal Gaussian fit to the MW data, indicating
the metal-rich (metal-poor) subpopulation. Overall we find that the Auriga 
simulations produce (sub)populations of GC candidates that are more metal-rich 
than the MW and M31 GC systems. The only exception is Au4-1 with $\mu \approx -1.51$
and $\sigma \approx 0.54$, close to the mean of the blue/metal-poor population
of the MW GCS. However, the insitu GC candidates in Au4-1 consists 30 times
less star particles than any of the other (sub)population. Finally, we find that
the populations of GC candidates that have formed insitu have mean values that 
are similar the that of the red/metal-rich subpopulation of Milky Way GCs.

(sub)populations of GC candidates in the Auriga simulations has a metallicity
distribution with sufficiently low

\begin{figure}
    \includegraphics[width=\columnwidth]{{logMFeH_withRatios-trim}.png}
    \caption{
        Mass-weighted metallicity distribution of star particles in the Auriga
        simulations. We show the median value of all Auriga haloes for all
        stars (orange dotted) and globular cluster candidates (i.e. stars with
        age $>$~10~Gyr; orange solid). The latter sub set is further split up
        between stars that formed in-situ (blue solid), and those that were accreted
        (red solid). Shaded regions indicate the $1\sigma$ interval. The MW (M31)
        GCS is shown in purple (magenta). The middle (bottom) panel shows the
        ratio of the simulated mass to the mass in the MW (M31) GCS.
        \label{fig:FeH}
    }
\end{figure}
Figure~\ref{fig:FeH} shows the mass-weighted metallicity distribution of the
Auriga L4 haloes. Lines show the median value and the shaded regions indicate
the $1\sigma$ interval around it (i.e. scatter between runs with different initial
conditions which thus have unique merger histories). We notice again that
the peak metallicity shifts down from $0$ to $-0.5$ for old stars (orange solid)
compared to all stars (orange dotted) while the mass at the peak lowers by 
roughly one dex. The mass budget of the old stars is
dominated by the old insitu population (blue solid) below [Fe/H]=$-1$, and by
the old accreted stars (red solid) above this value. We show the MW (M31) GCS 
in purple (magenta) and we show the ratio of the simulated to the observed 
profiles in the middle (bottom) panel. This mass excess can be thought of as a
combination of the bound cluster formation efficiency and disruptive processes,
further discussed in Sec.~\ref{sec:discussion_mass_excess}.

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{{logMRgc_withRatios-trim}.png}
    \caption{
        Mass-weighted radial distribution of star particles in the Auriga
        simulations. We show the median value of all Auriga haloes for all
        stars (orange dotted) and globular cluster candidates (i.e. stars with
        age $>$~10~Gyr; orange solid). The latter sub set is further split up
        between stars that formed in-situ (blue solid), and those that were accreted
        (red solid). Shaded regions indicate the $1\sigma$ interval. The MW (M31)
        GCS is shown in purple (magenta). The middle (bottom) panel shows the
        ratio of the simulated mass to the mass in the MW (M31) GCS.
        \label{fig:Rgc}
    }
\end{figure}
Figure~\ref{fig:Rgc} shows the mass-weighted radial distribution of the
Auriga L4 haloes. We notice a subtle peak around $10$~kpc for all star
particles that is not present for the old star particles, indicating that the
stellar disc is no longer present when applying the latter selection criterion.
Furtermore, we find that the dominant contribution to the total mass in old
stars changes from those formed insitu to the accreted population around 
$10$~kpc. We further discuss our comparison between the simulations and the 
observations in Sec.~\ref{sec:discussion_Rgc}.

>>>>

\subsection{Metallicity distribution}
\label{sec:results_FeH}
We investigate whether the star formation model implemented in Auriga produces 
metallicity distributions consistent with the MW (M31) GC system, and whether 
the subgrid generates sufficient total mass at metallicities (and radii) typical
for the MW (M31) GCS.

\begin{figure*}
    \includegraphics[width=\columnwidth]{{Au4-10_FeH_cleaner-trim}.png}
    \includegraphics[width=\columnwidth]{{Au4-21_FeH_cleaner-trim}.png}
    \caption{
        \emph{Left:} Metallicity distribution of Au4-10 (bottom panel). We show 
        the the GG candicates in green. We split the GC candidates into two 
        subpopulations, those that have formed insitu (blue), and those that have 
        been accreted (red). The thin green line shows all star particles.
        The solid purple (magenta) line in the top panel shows the GC system 
        of the MW (M31). \emph{Right:} Total mass in each metallicity bin.
        \label{fig:Au4-10and21_FeH}
    }
\end{figure*}
Figure~\ref{fig:Au4-10and21_FeH} shows the normalized metallicity distribution 
of Au4-10\footnote{The nomenclature is `Au' for Auriga, followed by the resolution 
level (4) and halo number (10 - indicating which set of initial conditions was 
used the run).} and Au4-21, showing the GC candidates in green. The accreted GC 
candidates are shown in red, and the insitu subpopulation in blue. The top panels 
show the MW (M31) GC system in purple (magenta). We overplot a double Gaussian 
for the MW GCS (the purple dashed lines), adopting literature values of the 
mean $\mu$ and standard deviation $\sigma$ of the metal-rich and metal-poor 
populations \citep[][p. 38]{Harris2001}.

We find that the age cut lowers the mean metallicity from $\sim 0.0$ to $\sim -0.6$.
Furthermore, the old accreted stars generally have lower metallicities than the
old insitu stars. The difference between the mean metalicity of the old insitu 
and old accreted stars for the majority of the simulations is $\sim 0.3$ (e.g.
Au4-21), and $\sim 0.5$ dex for Au4-10, Au4-16, Au4-17, Au4-18 and Au4-22.
This trent is only reversed for Au4-1 and Au4-4, for which the old insitu population
has a lower mean metallicity instead. For Au4-1 we find $\mu = -1.51$ (-0.74) 
for the old insitu (accreted), but the former consists of only 1019 particles 
(with a total mass of 5e7 M\Sun). Overall we find that the simulations produce 
(sub)populations of GC candidates that are more metal-rich than the MW and M31 
GC systems. Moreover, none of the simulations has a population of GC candidates 
with a bimodal metallicity distribution (the green curves).

\begin{figure}
    \includegraphics[width=\columnwidth]{{FeH_mu_sigma-trim}.png}
    \caption{
        First vs second central moment of the Auriga L4 metallicity distributions.
        Each cross represents one simulation for a given colour. The green (blue) 
        [red] crosses show the values calculated using the old (old insitu) 
        [old accreted] star particles. Green triangles indicate that all stars 
        were used. The purple (magenta) cross denotes our calculation using all 
        MW (M31) observations (i.e. asuming a unimodal distribution). The black 
        solid (open) dots indicate the literature values of a bimodal Gaussian 
        fit to the data \citep[values from][p. 38]{1998gcs..book.....A},
        showing the the metal-rich (metal-poor) component of the MW.
        \label{fig:FeH_mu_sigma}
    }
\end{figure}

We show the mean metallicity and standard deviation of all thirty Auriga L4 haloes
in Figure~\ref{fig:FeH_mu_sigma}. The green crosses are to be compared to the 
purple (magenta) cross, which shows the mean value of all MW (M31) GCs. 
We test the null hypothesis that MW (M31) and the GC candidates (all, insitu, and
accreted) are drawn from the same underlying distribution by calculating the KS
test statistic (i.e. six KS tests per simulation). We reject $H_0$ at the 100.00~\%
confidence level for virtually all subsets of all simulations, both for MW and M31,
except when comparing the old accreted stars of Au4-10 to the MW GCS. In this 
case we still reject $H_0$ with, but with $\leq 98.68$~\% confidence. When comparing
to the M31 GCS, the `best' matches are the old accreted subpopulations of Au4-13,
Au4-15, and Au4-17 ($H_0$ rejected with $\leq$ 99.82~\% confidence, 99.95~\%, 
and 98.32~\%). Here we find that the cumulative distributions are more or less 
similar up to [Fe/H]~$\sim$~-0.5, above which the simulations yield higher number 
counts which drives the KS test statistic over the critical values. This affirms
our finding that the simulations produce GC candidates that are more metal-rich 
than the MW (M31) GCS because under-production of old stars with [Fe/H]~$\leq$~-1.5,
and over-production of stars with [Fe/H]$\geq$~-0.5, are the main reason reasons
that $H_0$ is rejected with such high confidence.

In addition, we show the metal-rich (metal-poor) population of the MW GCS using 
a solid (open) dot. The mean metallicities of the old insitu populations appear
roughly consistent with that of the metal-rich population of the MW, but the 
simulations show larger dispersions.

\begin{figure}
    \includegraphics[width=\columnwidth]{{logMFeH_withRatios-trim}.png}
    \caption{
        Mass-weighted metallicity distribution of star particles in the Auriga
        simulations. We show the median value of all Auriga haloes for all
        stars (green dotted) and globular cluster candidates (i.e. stars with
        age $>$~10~Gyr; green solid). The latter sub set is further split up
        between stars that formed in-situ (blue solid), and those that were accreted
        (red solid). Shaded regions indicate the $1\sigma$ interval. The MW (M31)
        GCS is shown in purple (magenta). The middle (bottom) panel shows the
        ratio of the simulated mass to the mass in the MW (M31) GCS.
        \label{fig:FeH}
    }
\end{figure}
Figure~\ref{fig:FeH} shows the mass-weighted metallicity distribution of the
Auriga L4 haloes. Lines show the median value and the shaded regions indicate
the $1\sigma$ interval around it (i.e. scatter between runs with different initial
conditions which thus have unique merger histories). We notice again that
the peak metallicity shifts down from $0$ to $-0.5$ for old stars (green solid)
compared to all stars (green dotted) while the mass at the peak lowers by 
roughly one dex. The mass budget of the old stars is
dominated by the old insitu population (blue solid) below [Fe/H]=$-1$, and by
the old accreted stars (red solid) above this value. We show the MW (M31) GCS 
in purple (magenta) and we show the ratio of the simulated to the observed 
profiles in the middle (bottom) panel. This mass excess can be thought of as a
combination of the bound cluster formation efficiency and disruptive processes,
further discussed in Sec.~\ref{sec:discussion_mass_excess}.

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{{logMRgc_withRatios-trim}.png}
    \caption{
        Mass-weighted radial distribution of star particles in the Auriga
        simulations. We show the median value of all Auriga haloes for all
        stars (green dotted) and globular cluster candidates (i.e. stars with
        age $>$~10~Gyr; green solid). The latter sub set is further split up
        between stars that formed in-situ (blue solid), and those that were accreted
        (red solid). Shaded regions indicate the $1\sigma$ interval. The MW (M31)
        GCS is shown in purple (magenta). The middle (bottom) panel shows the
        ratio of the simulated mass to the mass in the MW (M31) GCS.
        \label{fig:Rgc}
    }
\end{figure}
Figure~\ref{fig:Rgc} shows the mass-weighted radial distribution of the
Auriga L4 haloes. We notice a subtle peak around $10$~kpc for all star
particles that is not present for the old star particles, indicating that the
stellar disc is no longer present when applying the latter selection criterion.
Furtermore, we find that the dominant contribution to the total mass in old
stars changes from those formed insitu to the accreted population around 
$10$~kpc. We further discuss our comparison between the simulations and the 
observations in Sec.~\ref{sec:discussion_Rgc}.
